Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2019-03-01 documentation/report.tex
Minor grammar edits

My objective was to develop accurate machine learning algorithms that are more accurate, and I succeeded at this goal! I composed a 28-page research whitepaper \cite{me} about my work on PICO-60, which has been reviewed and approved by the PICO collaboration and pre-published at \url{https://arxiv.org/abs/1811.11308}. It is currently undergoing peer review for eventual publication in the journal \textit{Computer Physics Communications}.

@@

For PICO-60, my intent was to develop a highly accurate classification algorithm that is intolerant to substantial impurities in calibration data. I developed and compared two sets of classification algorithms: supervised learning, and semi-supervised learning.

@@

\begin{figure}[ht]
    \centering
    \fbox{\includegraphics[width=0.95\textwidth]{pico_final_results}}
    \caption{\label{pico_final_results} Validation accuracy, precision, recall, and loss for each technique in PICO-60. Error bars represent the 8th and 92nd percentiles.}
\end{figure}

@@

\begin{itemize}
    \item Identification of neck alphas with 99.6\% precision (same as the conventional classifier).
    \item Reduction in the rate of false positives (simulated WIMP events misidentified as neck alphas) compared to the 91.0\% result achieved with a conventional classifier.
\end{itemize}

@@

\begin{figure}[ht]
    \centering
    \definecolor{lightcyan}{rgb}{0.8, 1, 1}
    \begin{tabular}[b]{|l|l|l|l|}
        \hline
        \rowcolor{lightcyan}
        Technique & Data Source & Background & False Positive Rate \\
        \rowcolor{lightcyan}
        & & Removal Rate & (WIMP Misclassifications) \\
        \hline
        Conventional Classifier & Simulation & 99.6\% & 91.0\% \\
        \hline
        Dense Neural Network & Simulation & 100\% & 100\% \\
        \hline
        Cylindrical Projection & Simulation & 99.9\% & 76.7\% \\
        \hline
        Topological CNN & Simulation & 99.9\% & 93.0\% \\
        \hline
        Cylindrical Projection & Simulation (Test) & 99.6\% & 75.7\% \\
        \hline
        Cylindrical Projection & Real-World & 91.2\% & 73.9\% \\
        \hline
    \end{tabular}
    \caption{\label{deap_final_results} Average background and WIMP/neutron removal rates for the highest-accuracy hyperparameter configuration of each technique in DEAP-3600.}
\end{figure}

>>>>

My objective was to develop machine learning algorithms that are more accurate, and I succeeded at this goal! I composed a 28-page research whitepaper \cite{me} about my work on PICO-60, which has been reviewed and approved by the PICO collaboration and pre-published at \url{https://arxiv.org/abs/1811.11308}. It is currently undergoing peer review for eventual publication in the journal \textit{Computer Physics Communications}.

@@

For PICO-60, my intent was to develop a highly accurate classification algorithm that is tolerant to substantial impurities in calibration data. I developed and compared two sets of classification algorithms: supervised learning, and semi-supervised learning.

@@

\begin{figure}[ht]
    \centering
    \fbox{\includegraphics[width=0.85\textwidth]{pico_final_results}}
    \caption{\label{pico_final_results} Validation accuracy, precision, recall, and loss for each technique in PICO-60. Error bars represent the 8th and 92nd percentiles.}
\end{figure}

@@

\begin{itemize}
    \item Identification of neck alphas with a minimum of 99.6\% precision (the same as the previously developed conventional classifier).
    \item Reduction in the rate of false positives (simulated WIMP events misidentified as neck alphas) compared to the 91.0\% result achieved with a conventional classifier.
\end{itemize}

@@

\begin{figure}[ht]
    \centering
    \definecolor{lightcyan}{rgb}{0.8, 1, 1}
    \begin{tabular}[b]{|l|l|l|l|}
        \hline
        \rowcolor{lightcyan}
        Technique & Data Source & Background & False Positive Rate \\
        \rowcolor{lightcyan}
        & & Removal Rate & (WIMP Misclassifications) \\
        \hline
        Conventional Classifier & Simulation (Val.) & 99.6\% & 91.0\% \\
        \hline
        Dense Neural Network & Simulation (Val.) & 100\% & 100\% \\
        \hline
        Cylindrical Projection & Simulation (Val.) & 99.9\% & 76.7\% \\
        \hline
        Topological CNN & Simulation (Val.) & 99.9\% & 93.0\% \\
        \hline
        Cylindrical Projection & Simulation (Test) & 99.6\% & 75.7\% \\
        \hline
        Cylindrical Projection & Real-World & 91.2\% & 73.9\% \\
        \hline
    \end{tabular}
    \caption{\label{deap_final_results} Average background and WIMP/neutron removal rates for the highest-accuracy hyperparameter configuration of each technique in DEAP-3600.}
\end{figure}
